---
title: "SimpleRegress"
author: "Christina Jones"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

We are comparing the variables CHEST and NECK to see which is better at predicting the LENGTH of a bear. 



## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

This scatter plot and numerical summary of the variables of NECK and LENGTH. The adjusted R squared is at 0.7476. 
As the circumference of the neck increases so does the length of the bear. 


## now predict the length of a bear who has a neck of 17, 22 and 26



```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE, interval = "prediction")
```

This numerical summary is the prediction of the length of a bear when the neck is at 17, 22, and 26. 


## Nurerical Results

```{r}
cor(bears$LENGTH,bears$NECK)
```

This is the correlation coefficient of LENGTH and NECK.









## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

## Model LENGTH ~ CHEST


```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```


## Numerical Summary 


```{r}
cor(bears$LENGTH,bears$CHEST)
```
This is the correlation coefficient of LENGTH and .



## Conclusion 

CHEST is a better variable to use to predict for the length of bears because the adjusted R squared test shows for chest is at 0.7869. The adjusted R squared of the fit using CHEST is larger than the adjusted R squared of the fit using NECK




